Exploiting the Graph: Increasing Engagement in Collaborative Interactive Evolution

### 2017-01-25 2017-CEC-Graph-Based-Population-For- IEC/paper.tex
Neo4J

Using the Noe4J graph database and the Cypher query language when monitoring the experiments provided 
views on the connected data difficult to replicate in a relational database. As an example, when comparing the
deployments B and GG based on their network of users (shown in figures \ref{fig:B-network} and \ref{fig:GG-network}
respectivly) additionaly to the differences in the number of nodes, certain patterns can also be observed.

>>>>

Using the Neo4J graph database and the Cypher query language when monitoring the experiments provided 
views on the connected data difficult to replicate in a relational database. As an example, when comparing the
deployments B and GG based on their network of users (shown in figures \ref{fig:B-network} and \ref{fig:GG-network}
respectivly) additionaly to the differences in the number of nodes, certain patterns can also be observed.
